Monte Carlo and bootstrap for all parameters

### 2024-08-07 MC3_all.Rmd
Radii

In this document, \textbf{uniform sampling} is used to create a sample and \textbf{three circles} with a radii of 6, 9 and 15 are used to compute local variables.

>>>>

In this document, \textbf{uniform sampling} is used to create a sample and \textbf{three circles} with radii of 6, 9 and 15 are used to compute local variables.
